---
title: "data through web scraping"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output:
  html_document:
    self_contained: no
    toc: yes
    toc_depth: 3
    toc_float: 
      collapsed: false
---

```{r child = "setup.Rmd"}
```

## Scope
The source of data were blogs 

### Blogs

1. https://edublogs.org 
2. https://www.blogger.com

[https://edublogs.org/robots.txt](https://edublogs.org/robots.txt)

[https://developers.google.com/blogger](https://developers.google.com/blogger)


1.	Go to Google.com.
2.	Enter site:www.website.com and 'Search Term' into the search box.
3.	Refine your search.



Find Blogs on Blogger through Google web search. To find a blogger on Google you have to make the following queries in to the Google.

`site:blogger.com Search_Term`  
OR  
`site:blogspot.com Search_Term`  
OR
`site:edutopia.org covid virtual pedagogy` 



[site:blogger.com distance education](https://www.google.com/search?client=firefox-b-d&q=site%3Ablogger.com+distance+education)  
OR
[site:edublogs.org covid pedagogy](https://www.google.com/search?q=site%3Aedublogs.org+covid+pedagogy)

`site:edutopia.org covid virtual pedagogy` 
https://www.edutopia.org/terms-of-use





https://visualisingideas.edublogs.org/2020/03/
https://scis.edublogs.org/tag/remote-learning/

https://www.blog.google/outreach-initiatives/education/distancelearning-covid19/
https://www.blog.google/outreach-initiatives/education/social-emotional-learning-covid19/ 
https://gemreportunesco.wordpress.com/2020/04/01/covid-19-wheres-the-discussion-on-distance-learning-training-for-teachers/


```{r}
# https://towardsdatascience.com/tidy-web-scraping-in-r-tutorial-and-resources-ac9f72b4fe47

if (!("rvest" %in% installed.packages())) {
 install.packages("rvest")
}

if (!("dplyr" %in% installed.packages())) {
 install.packages("dplyr")
}

library(rvest)
library(dplyr)
```



```{r}
hot100page <- "https://www.billboard.com/charts/hot-100"
hot100 <- read_html(hot100page)

hot100
str(hot100)
```

```{r}
#  list of nodes inside the body of the page.
body_nodes <- hot100 %>% 
 html_node("body") %>% 
 html_children()

body_nodes
```

```{r}
rank <- hot100 %>% 
  rvest::html_nodes('body') %>% 
  xml2::xml_find_all("//span[contains(@class, 'chart-element__rank__number')]") %>% 
  rvest::html_text()

artist <- hot100 %>% 
  rvest::html_nodes('body') %>% 
  xml2::xml_find_all("//span[contains(@class, 'chart-element__information__artist')]") %>% 
  rvest::html_text()

title <- hot100 %>% 
  rvest::html_nodes('body') %>% 
  xml2::xml_find_all("//span[contains(@class, 'chart-element__information__song')]") %>% 
  rvest::html_text()

chart_df <- data.frame(rank, artist, title)

knitr::kable(
  chart_df  %>% head(10))

```








### Twitter (threads)

@threadreaderapp 'unroll'
[Twitter thread vy @YaeganDoran](https://threadreaderapp.com/thread/1272337288249217025.html)








